Quality assurance of digital twins -- An experience report in the automotive industry

### 2022-12-06 manuscripts/paper-1/main.tex
refine paper outline

    \section{Introduction}
    \label{section:introduction}
    TODO~\cite{Boschert2016,Fuller2020,Jones2020}

    \section{What is a digital twin?}
    TODO

    \subsection{Methodology}
    TODO

    \subsection{Result}
    TODO

    \subsection{Validation}
    TODO

    \section{What is digital twin quality?}
    TODO

    \subsection{Methodology}
    TODO

    \subsection{Result}
    TODO

    \subsection{Validation}
    TODO

    \section{What are digital twin quality issues?}
    TODO

    \subsection{Methodology}
    TODO

    \subsection{Result}
    TODO

    \subsection{Validation}
    TODO

@@

>>>>

    \section{Introduction}\label{section:introduction}

    Cyber-physical system (CPS), is a conceptual architecture/approach which aims to conjoin the physical and virtual space. 
    The aim of the CPS is to integrate communication and computing capabilities to physical assets to monitor, coordinate and control the physical space (where the physical assets exist) from the virtual space (where the virtual models exist), while achieve seamless real-time connection between the spaces.
    Digital twin approach is on the other hand, is a pragmatic solution, which is the execution of the CPS.~\cite{TAO20193}

    First occurrence of "Digital Twin" term  was introduced by Dr.~Michael Grieves in 2003 at the University of Michigan while giving  Product Lifecycle Management(PLM) course.~\cite{article}
    His introduction to term was rather raw, but still introduced a pragmatic solution to uncoupled solutions of global manufacturers, which were working only with physical or virtual products.

    His approach had three dimensions, along with a physical entity, a virtual entity and a connection between these entities which constructed the main frame for the today's evaluating digital twins.~\cite{article}

    Physical entity exists in the physical space with real functionalities and performance. They are responsible to accomplish certain tasks within the physical space, to give certain outputs.
    Different levels of abstraction can be usable for a physical entity such as an electric motor in the 1/10 of an RC Car, bearings in a certain machine, solar panels above some construction, human or an entire world can be counted as an example of a physical entity.
    Virtual entity exists in the virtual space with

    With the improvement

    %/TODO SHOULD WE EXPLAIN OUR DIGITAL TWIN HERE?

    \subsection{Research objectives}

    Find approach for assessing the quality of digital twins...

    \subsection{Research questions}

    What is quality of digital twins? What is good quality? What is bad quality? What is impact of good quality? What is impact of bad quality? What are typical quality issues? How to assess quality? ...

    \subsection{Scientific contributions}

    Literature review (see Section~\ref{section:literature}), case study (see Section~\ref{section:case})...

    \section{Literature review}
    \label{section:literature}

    Methodology (see Section~\ref{section:liteature_methodology}), result (see Section~\ref{section:liteature_result}), and summary (See Section~\ref{section:liteature_summary})...

    \subsection{Methodology}
    \label{section:liteature_methodology}

    How did we find existing literature?

    \begin{itemize}
        \item ("digital twin" OR "simulation model" OR "system model" OR "CAD model") AND (quality OR defect OR issue OR error)
        \item ("digital twin" OR "simulation model" OR "system model" OR "CAD model") AND (verification OR validation OR accreditation)
    \end{itemize}

    \subsection{Result}
    \label{section:liteature_result}

    What is existing literature?

    \subsection{Summary}
    \label{section:liteature_summary}

    What do we learn from existing literature?
    (Existing literature does at most partially solve our problem!)

    \section{Case study (FELICE)}
    \label{section:case}

    TODO (Explain limitations of the FELICE digital twin! It is not a complete digital twin according to literature! It includes this, it is missing this.)

    \subsection{Methodology}
    \label{section:case_methodology}

    TODO

    \subsection{Result}
    \label{section:case_result}

    TODO

    \subsection{Summary}
    \label{section:case_summary}

    TODO

@@

    \section*{Acknowledgements}
    TODO
